Exacerbated by the Pandemic: Analyzing the Impact of COVID-19 on Mortality Among Toronto's Homeless by Gender Disparities

### 2024-03-17 paper/paper.qmd
paper.qmd

Homelessness is a serious challenge in Toronto, Canada, drawing attention to the harsh realities faced by the most vulnerable groups. The health vulnerabilities and mortality rates of homeless individuals are alarmingly high when compared to the general population. Within Toronto's male homeless community that uses shelters, the mortality rate for those aged 18-24 is 8.3 times higher, for ages 25-44 it is 3.7 times, and for those 45-64 it is 2.3 times the rate of their housed counterparts. For homeless women aged 18-44, the risk of death is 10-fold compared to the average woman in Toronto (Hwang 2001). Pre-existing burdens of mental illness, substance dependence, various medical conditions, infectious diseases, and physical trauma have been compounded since December 2019 by the advent of COVID-19, further endangering those in communal living situations.

>>>>

Homelessness is a serious challenge in Toronto, Canada, drawing attention to the harsh realities faced by the most vulnerable groups. The health vulnerabilities and mortality rates of homeless individuals are alarmingly high when compared to the general population. Pre-existing burdens of mental illness, substance dependence, various medical conditions, infectious diseases, and physical trauma have been compounded since December 2019 by the advent of COVID-19, further endangering those in communal living situations.
